Peer Assessment 1
=====================
Loading and preprocessing the data


1 Load the data (i.e. read.csv()).

2 Process/transform the data (if necessary) into a format suitable for your analysis.


```{r LoadDataset}
setwd("~/Desktop/Coursera/Reproducible Research/Peer Assessment 1")
data<-read.csv("activity.csv")
```

# What is mean total number of steps taken per day?

All missing values in the dataset are ignored.

1 Make a histogram of the total number of steps taken each day

```{r DailystepHistogram}
Dailysteps<-tapply(data$steps,data$date,sum)
hist(Dailysteps)
```

2 Calculate and report the mean and median total number of steps taken per day
```{r Mean & Median}
Mean<-tapply(data$steps,data$date,mean)
Median<-tapply(data$steps,as.character(data$date),median)
Mean
Median
```

## What is the average daily activity pattern?

1 Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)

```{r TimeSeriesPlot}
data1<-data[order(data$interval),]
data2<-na.omit(data1)
NoOfinterval<-numeric(0)
sum<-numeric(0)
interval<-unique(data2$interval)
for (i in interval) {
        intervaldataset<-subset(data2,data2$interval==i)
        NoOfinterval<-c(NoOfinterval,nrow(intervaldataset))
        sum<-c(sum,sum(intervaldataset$steps))
}
interval_mean<-sum/NoOfinterval
plot(interval,interval_mean,type="l")
```

2 Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?

```{r Max_5-minuteInterval}
intervalmeanchar<-as.character(interval_mean)
maxno<-grep(as.character(max(interval_mean,na.rm=T)),intervalmeanchar)
Max_5minuteInterval<-interval[[maxno]] ###### This is the value of the Max_5-minuteInterval
Max_5minuteInterval
```

### Imputing missing values

1 Calculate and report the total number of missing values in the dataset (i.e. the total number of rows with NAs)

```{r NoofNAsrow}
totalrow<-nrow(data)
completedrow<-nrow(na.omit(data))
NAsrow<-totalrow-completedrow  ##### This is the total number of rows with NAs. 
NAsrow
```

2 Devise a strategy for filling in all of the missing values in the dataset. The strategy does not need to be sophisticated. For example, you could use the mean/median for that day, or the mean for that 5-minute interval, etc.

```{r dataset with the mean for that 5-minute interval filling for NA}
table<-data.frame(rep(interval_mean,61))  ##### Replicate the interval means for 61 times, 
                                          ##### because there are 61 days in the dataset. 
colnames(table)<-c("mean")

data_new<-cbind(data,table)

data_new$label<-is.na(data_new$steps) ##### Create a factor "is.na"" label 
colnames<-colnames(data_new)
data_split<-split(data_new,data_new$label) ##### Split the dataset into two datasets 
                                           ##### based on "is.na" label 
data_split1<-data.frame(data_split[1])
colnames(data_split1)<-colnames
data_split2<-data.frame(data_split[2])
colnames(data_split2)<-colnames
data_split2[,1]<-data_split2[,4]
data_new<-rbind(data_split1,data_split2)
data_new<-data_new[,1:3]
data_new<-data_new[order(data_new$date),]

############repeat the steps in Section "What is mean total number of steps taken per day?"
Dailysteps_new<-tapply(data_new$steps,data_new$date,sum)
hist(Dailysteps_new)
```

3 Calculate and report the mean and median total number of steps taken per day in the new dataset
```{r New Mean & Median}
Mean<-tapply(data_new$steps,data_new$date,mean)
Median<-tapply(data_new$steps,as.character(data_new$date),median)
Mean
Median
```

#### Are there differences in activity patterns between weekdays and weekends?

1 Create a new factor variable in the dataset with two levels – “weekday” and “weekend” indicating whether a given date is a weekday or weekend day.
```{r dataset with a “weekday” and “weekend” indicator variable }
data_new$date<-strptime(as.character(data_new$date),"%Y-%m-%d")
data_new$weekday<-weekdays(data_new$date)
data_new$week<-ifelse(data_new$weekday %in% c("Satuday", "Sunday"),
       data_new$week <-"Weekend", data_new$week <-"Weekday")
```


2 Make a panel plot containing a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all weekday days or weekend days (y-axis). 

```{r New TimeSeriesPlot }


data1<-data_new[order(data_new$interval),]
NoOfinterval<-numeric(0)
sum<-numeric(0)
interval<-unique(data1$interval)
for (i in interval) {
        intervaldataset<-subset(data1,data1$interval==i)
        NoOfinterval<-c(NoOfinterval,nrow(intervaldataset))
        sum<-c(sum,sum(intervaldataset$steps))
}
data1$mean<-sum/NoOfinterval
data_weekday<-subset(data1,data1$week=="Weekday")
data_weekend<-subset(data1,data1$week=="Weekend")
par(mar=c(4,4,0.3,0.3), mfcol=c(2,1))
plot(data_weekend$interval,data_weekend$mean,type="l",ylab="Number fo steps")
plot(data_weekday$interval,data_weekday$mean,type="l",ylab="Number fo steps")
```
